Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-07-21 docs/paper/paper.Rmd
tweak

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as "epiforecasts-EpiNow2" by the hub), and our surrogate model (referred to as "epiforecasts-weeklygrowth" by the hub). Of the remaining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r length(partial_models)` models submitted for between 3 and 30 locations and all these models varied the number of locations they submitted forecasts for over time, potentially indicating manual curation or models targted at specific conditions.

>>>>

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as `epiforecasts-EpiNow2` by the hub), and our surrogate model. Of the remaining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r length(partial_models)` models submitted for between 3 and 30 locations and all these models varied the number of locations they submitted forecasts for over time, potentially indicating manual curation or models targeted at specific conditions.
